Tables/Graphs for Article

### 2018-01-14 article/graphics.Rmd
added data frame of final model hazard, SE, CI

# ------------------------------------------
# data frame with coefficients, HR and confidence intervals
# SE of all coefficients 
se <- c(0.0476, 0.0904, 0.0784, 0.0830, 0.0697, 0.0555, 0.0597, 0.0815, 0.0695, 0.0364, 0.0340, 0.0422, 0.0332, 0.0499, 0.0645, 0.0857, 0.0362, 0.0331, 0.7204, 0.1856, 0.8452, 4.1705, 6.8973, 0.1062, 0.6381, 2.5243, 0.2496, 2.5575, 7.4036, 10.2644, 0.4776, 0.7266)

coefficientsdf <- data.frame(coefficients = names(model$coefficients), 
                             beta = as.numeric(unname(model$coefficients)),
                             SE = se,
                             HR = exp(coefficientsdf$beta),
                             upper = exp(coefficientsdf$beta + (1.96*coefficientsdf$SE)),
                             lower = exp(coefficientsdf$beta - (1.96*coefficientsdf$SE))
                             )

@@

final_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = metric$stats[3], 
                              pval = metric$stats[5],
                              R2 = metric$stats[8],
                              AIC = stats::AIC(metric, k = 2),
                              Dxy = metric$stats[9], 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
final_metrics
xtable::xtable(final_metrics, caption = "Performance metrics for model fit to the full data", label = "table:finalmetrics", digits = 4)

# ------------------------------------------
# proportional hazards assumptions
ph <- cox.zph(model)
ph_test <- data.frame(predictors = rownames(ph$table), ph$table)
rownames(ph_test) = NULL
ph_test <- ph_test %>% arrange(p) 
ph_test

```

>>>>

# ------------------------------------------
# df with coefficients, HR and confidence intervals
# SE of all coefficients 
se <- c(0.0476, 0.0904, 0.0784, 0.0830, 0.0697, 0.0555, 0.0597, 0.0815, 0.0695, 0.0364, 0.0340, 0.0422, 0.0332, 0.0499, 0.0645, 0.0857, 0.0362, 0.0331, 0.7204, 0.1856, 0.8452, 4.1705, 6.8973, 0.1062, 0.6381, 2.5243, 0.2496, 2.5575, 7.4036, 10.2644, 0.4776, 0.7266)

coefficientsdf <- data.frame(coefficients = names(model$coefficients), 
                             beta = as.numeric(unname(model$coefficients)),
                             SE = se
                             )
coefficientsdf$HR <- exp(coefficientsdf$beta)
coefficientsdf$upper <- exp(coefficientsdf$beta + (1.96 * coefficientsdf$SE))
coefficientsdf$lower <- exp(coefficientsdf$beta - (1.96*coefficientsdf$SE))

@@

final_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = metric$stats[3], 
                              pval = metric$stats[5],
                              R2 = metric$stats[8],
                              AIC = stats::AIC(metric, k = 2),
                              Dxy = metric$stats[9], 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = x)$concordance)
final_metrics

# ------------------------------------------
# proportional hazards assumptions
ph <- cox.zph(model)
ph_test <- data.frame(predictors = rownames(ph$table), ph$table)
rownames(ph_test) = NULL
ph_test <- ph_test %>% arrange(p) 
ph_test
```
